---
title: "NYPD Shooting Incident Data"


output:
  pdf_document: default
  html_document:
    df_print: paged
---
Loading Libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(ggplot2)
```

Importing Data
I will start by reading in the data from the CSV file by using the link
from <https://catalog.data.gov/dataset>



```{r import_data, message=FALSE}
NYPD_shooting_data <- read.csv(url("https://data.cityofnewyork.us/api/views/833y-fsy8/rows.csv?accessType=DOWNLOAD"))
```

## Reading the dataset to see what we got.

Will be using the head function to see the first 5 rows of the dataset. 

```{r head}
head(NYPD_shooting_data,5)
```
##Changing the Data Frame.

After looking through the data, I decided to keep: Date, Boro, Perp_Age_group, Perp_sex, Perp_Race, Vic_Age_group, Vic_sex,and Vic_RAce

```{r}
NYPD_New <- NYPD_shooting_data[c("OCCUR_DATE", "OCCUR_TIME", "BORO", "PERP_AGE_GROUP", "PERP_SEX", "PERP_RACE", "VIC_AGE_GROUP", "VIC_SEX", "VIC_RACE")]
```

Renaming the columns so that they are more easily readable. Transforming all the blank columns into NA.

```{r}
colnames(NYPD_New) <- c("Date", "Time", "Region", "Attacker_Age_Group", "Attacker_Gender", "Attacker_Race", "Victim_Age", "Victim_Gender", "Victim_Race")
NYPD_New[NYPD_New==""]<-NA

NYPD_New<-NYPD_New %>%
  mutate(Date = mdy(Date))

head(NYPD_New,5)

```
```{r}
#replacing Attacker Gender
NYPD_New$Attacker_Gender[NYPD_New$Attacker_Gender =="M"] <- 1
NYPD_New$Attacker_Gender[NYPD_New$Attacker_Gender =="F"] <- 0
NYPD_New$Attacker_Gender[NYPD_New$Attacker_Gender =="U"] <- NA

#replacing Victim Gender
NYPD_New$Victim_Gender[NYPD_New$Victim_Gender =="M"]<-1
NYPD_New$Victim_Gender[NYPD_New$Victim_Gender =="F"]<-0

#Replacing Attacker Age Group
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="<18"] <- 0
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="18-24"] <- 1
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="25-44"] <- 2
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="45-64"] <- 3
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="65+"] <- 4
NYPD_New$Attacker_Age_Group[NYPD_New$Attacker_Age_Group=="UNKNOWN"] <- NA

#Replacing Victim Age Group
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="<18"] <-0
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="18-24"] <-1
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="25-44"] <-2
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="45-64"] <-3
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="65+"] <-4
NYPD_New$Victim_Age[NYPD_New$Victim_Age=="UNKNOWN"] <-NA
```



Creating a bar plot to see where the most shooting incidents occur. By this plot, we can easily see Brooklyn has the most shooting incidents.  

```{r}
barplot(table(NYPD_New$Region), main = "Number of Crimes per Region in NYC", las = 1)
```

```{r}
barplot(table(NYPD_New$Attacker_Age_Group), horiz = T, xlab = "Count", ylab = "Age Group", las =1, main = "Attacker Age Group")
barplot(table(NYPD_New$Victim_Age), horiz = T, xlab = "Count", ylab = "Age Group", las =1, main = "Victim Age Group")
```
```{r}
barplot(table(NYPD_New$Victim_Gender), xlab = "Gender:0=F, 1=M", main = "Victim Gender")
barplot(table(NYPD_New$Attacker_Gender), xlab = "Gender:0=F, 1= M", main = "Attacker Gender")
```

```{r}


#using only columns that i want to use
for_model <- NYPD_New[c("Attacker_Gender", "Victim_Gender", "Attacker_Age_Group", "Victim_Age")]

mod1 <- lm(Attacker_Age_Group ~ Victim_Gender + Victim_Age, data = for_model)

```

##Possible Bias Sources: Step 4
Conclusion to my project and include any possible sources of bias. Be sure to identify what your personal bias might be and how you have mitigated that. 
I view data for NYC as a whole rather than per borough.
I disregarded race of the victim, as that may have something to do with the attacker. 
